\documentclass{article}

\usepackage{cv}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{Wesley Bland}

\info{9700 South Cass Avenue\\
      Bldg. 240, Room: 3154 \\ 
      Argonne, Illinois 60439-4844\\
      Phone: (630) 252-1390\\
      Email: wbland@mcs.anl.gov\\
      WWW: www.mcs.anl.gov/~wbland
  } 

\bibliography{papers}

\addtocategory{subpapers}{Bland:CCPE:2013}
\addtocategory{techreports}{bland2012proposal}
\addtocategory{phd}{blandthesis}
\addtocategory{conferences}{Bland:Euro-Par:Resilience:2012,Bland:EuroMPI:2012,Bland:Euro-Par:2012}
\addtocategory{conferences}{Bland:2012:EAR:2310096.2310161,Naughton:2009:FIF:1552526.1552530}
\addtocategory{conferences}{Vallee:Virtualization:2008}
\addtocategory{conferences}{4215574,4215575}

\begin{document}
\maketitle

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EDUCATION}} 

{\sl Doctor of Philosophy}, Computer Science \\
University of Tennessee, Knoxville, TN \hfill May 2013 \\
 
{\sl Master of Science}, Computer Science \\ 
University of Tennessee, Knoxville, TN \hfill May 2009 \\

{\sl Bachelor of Science}, Computer Science\\ 
Tennessee Technological University, Cookeville, TN \hfill May 2007

%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PROFESSIONAL EXPERIENCE}} 

{\sl Postdoctoral Appointee, Argonne National Laboratory, Argonne, IL} \\
Dr. Pavan Balaji (balaji@mcs.anl.gov) \hfill April 2013 -- Present
\begin{itemize} \itemsep -2pt
        \item Lead implementation of ULFM in MPICH.
        \item MPICH developer.
        \item Design and implement fault tolerant libraries and applications.
\end{itemize}

{\sl Graduate Research Assistant, Innovative Computing Laboratory, University
of Tennessee, Knoxville, TN} \\
Dr. Jack Dongarra (dongarra@eecs.utk.edu), Dr. George Bosilca
(bosilca@eecs.utk.edu) \hfill August 2009 -- April 2013 
\begin{itemize} \itemsep -2pt % Reduce space between items
        \item Developed User Level Failure Mitigation (ULFM), a proposal to
            the MPI forum discussing fault tolerance in MPI, and the
            accompanying implemenation based on Open MPI.
        \item Developed Checkpoint-on-Failure (CoF), a fault tolerant protocol
            using MPI-3 techniques to checkpoint applications after a failure
            rather than periodically throughout the application lifecycle.
        \item Worked with various libraries and applications to help
            implement fault tolerance using ULFM.
\end{itemize}

{\sl Intern, Oak Ridge National Laboratory, Oak Ridge, TN} \\
Dr. Richard L. Graham (rlgraham@ornl.gov) \hfill May 2009 -- August 2010 
\begin{itemize} \itemsep -2pt % Reduce space between items
        \item Worked on the initial design and implementation for Scalable
            Tools Communications Infrastructure (STCI).
        \item Interacted with Open MPI development team to investigate
            integration of STCI.
\end{itemize} 
Dr. Stephen L. Scott (scottsl@ornl.gov) \hfill Summers 2005 -- 2008
\begin{itemize} \itemsep -2pt
        \item Implemented new features and bug fixes for Cluster Command and
            Control (C3).
        \item Impelemented command line installation interface for Open Source
            Cluster Application Resources (OSCAR).
        \item Investigated and implemented fault injection tools for virtual
            environments.
\end{itemize}
Dr. Walter Dykas \hfill Summer 2004
\begin{itemize} \itemsep -2pt
        \item Implemented log analyzer scripts to parse security logs and
            search for anomalies
\end{itemize}

{\sl Graduate Teaching Assistant, University of Tennessee, Knoxville, TN} \\
Dr. Jack Dongarra (dongarra@eecs.utk.edu) \hfill Spring Semester 2009
\begin{itemize} \itemsep -2pt
        \item Teaching assistant for CS 594 -- Scientific Computing for
            Engineers
        \item Assisted in lectures, grading assignments, and supervising
            laboratory activities.
        \item Led class construction of two Linux clusters.
\end{itemize}
Dr. David Straight (straight@eecs.utk.edu) \hfill Fall Semester 2007 -- Spring Semester 2008
\begin{itemize} \itemsep -2pt
        \item Teaching assistant for CS 100 -- Introduction to Computer
            Science
        \item Supervised and lectured for laboratories teaching basic computer
            science skills to non-majors.
        \item Spring 2008 -- Head TA, supervising all other TAs for the lab
            sections.
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	STUDENTS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{STUDENTS}}

{\sl Chaoran Yang} \hfill Summer 2013
%\begin{itemize}
%\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PUBLICATIONS}} 
\printbib{subpapers}
\printbib{books}
\printbib{papers}
\printbib{chapters}
\printbib{conferences}
\printbib{techreports}
\printbib{phd}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	HONORS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{HONORS}} 

\begin{itemize}
    \item Best Paper -- International European Conference on Parallel and Distributed Computing (Euro-Par) -- 2012
    \item Outstanding STARS Mentor -- University of Tennessee ACM Student Chapter -- 2012
    \item Outstanding Undergraduate Research Award -- Tennessee Technological University Research Day -- 2007
    \item Who's Who Among Students in American Universities -- 2007
    \item Dean's List -- Tennessee Technological University -- 2003 - 2007
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	SERVICE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{SERVICE}}

{\sl Professional}
\begin{itemize}
    \item MPI Forum -- Participant and member of Fault Tolerance Working Group -- 2012 - Present
    \item Reviewer -- Parallel Computing -- 2013
    \item Reviewer -- Heterogeneity in Computing Workshop -- 2012
    \item Reviewer -- International Parallel \& Distributed Processing Symposium -- 2012
    \item SCinet Student Volunteer - International Conference for High
        Performance Computing, Networking, Storage and Analysis -- 2009 - 2012
\end{itemize}

{\sl Electrical Engineering and Computer Science Department}
\begin{itemize}
    \item Mentor -- STARS Alliance Program -- 2011 - 2013
    \item President -- University of Tennessee ACM Student Chapter -- 2007 - 2008
\end{itemize}

%----------------------------------------------------------------------------------------
%	MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{MEMBERSHIPS}} 

\begin{center}
    Association for Computing Machinery -- 2004 - Present\\
    IEEE -- 2013 - Present
\end{center}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{INTERESTS}} 

\begin{center}
Fault Tolerance, Communication Runtimes, High Performance Computing, Distributed and Parallel Computing
\end{center} 


%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{COMPUTER SKILLS}}

MPI, C, \LaTeX, Java, Perl, Bash

%----------------------------------------------------------------------------------------

\end{document}
